Predicting Fire Risk: \\ An Evaluation of the Fire Danger Index

### 2016-05-13 paper.tex
Restructured to match journal requirements
start on restructuring paper

\section{Background and Literature Review}

@@

\section{Data}

@@

\subsection{Explanatory Variables}

We predict probability of ignition using McArthur's Forest Fire Danger Index (FFDI), the meteorological variables used as inputs for the FFDI, grassland curing, vapour pressure at 9am and rainfall.

@@

\subsection{Response Variable: Fire Occurrence}

\subsection{Assembling Datasets}

@@

\section{Method}

@@

@@

\subsection{Random Forests}

@@

\subsection{Classification with Unbalanced Classes}

@@

We add splines to Model 3 in stages using the confusion matrices for 10-fold cross validation to assess accuracy \citep[][using the caret package by]{caret}. The best performing model based on balanced accuracy and number of false negatives (incorrectly predicted `No Fires') is reported in Table~\ref{table:logf}.

@@

%GAM plots, not sure if this is exactly splines...
\begin{figure}
  \null\vfill\noindent
  %\includegraphics[page=1,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
  \hfill
  %\includegraphics[page=2,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
  \vfill
  %\includegraphics[page=3,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
  \hfill
  %\includegraphics[page=4,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
  \vfill
  %\includegraphics[page=5,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
  \hfill
  %\includegraphics[page=6,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
  \vfill
  \null
  \caption{Plots of smoothing functions in Model 4 with 95\% point-wise confident interval}
  \label{fig:gam_pl}
\end{figure}

@@

@@

>>>>

@@

\section{Methods}

Data was compiled from multiple sources to study the fire incidence, and two types of models were used to prdeict incidence on the basis of these variables.

\subsection{Data}

\subsubsection{Fire}

@@

@@

\subsubsection{Assembling Datasets}

@@

\subsection{Models}

\subsubsection{Logistic Regression}

@@

\subsubsection{Classification Trees}

@@

\subsubsection{Random Forests}

@@

\subsubsection{Classification with Unbalanced Classes}

@@

We add splines to Model 3 in stages using the confusion matrices for 10-fold cross validation to assess accuracy \citep[][using the caret package by]{caret}. The best performing model based on balanced accuracy and number of false negatives (incorrectly predicted `No Fires') is reported in Appendix (Table~\ref{table:logf}).

@@

%GAM plots, not sure if this is exactly splines...
%\begin{figure}
%  \null\vfill\noindent
  %\includegraphics[page=1,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
%  \hfill
  %\includegraphics[page=2,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
%  \vfill
  %\includegraphics[page=3,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
%  \hfill
  %\includegraphics[page=4,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
%  \vfill
  %\includegraphics[page=5,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
%  \hfill
  %\includegraphics[page=6,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
%  \vfill
%  \null
%  \caption{Plots of smoothing functions in Model 4 with 95\% point-wise confident interval}
%  \label{fig:gam_pl}
%\end{figure}

@@

\section*{Acknowledgements}

The R software~\citep{CRAN} was used to analyse the data, including the packages ggplot2~\citep{ggplot2}, ...

@@

\section*{Appendix}
